--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Windows 7 also need MiKTeX. Besides, there is a known issue with [MiKTeX](http://tex.stackexchange.com/questions/27138/how-can-i-fix-the-error-gui-framework-cannot-be-initialized-with-texniccenter) 

LaTeX terminates with "GUI framework cannot be initialized" if invoked from TeXnicCenter (1.0 Stable Release Candidate 1). This happens when a missing package needs to be installed and the pop-up window cannot be displayed.

Remedy: start MiKTeX Options and choose either Yes or No (but not "Ask me first") for the option "Install missing packages on-the-fly".

Perl also should be installed for epub format.

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
